\chapter{Forward}

A word about some of the authors, their backgrounds and their motivations.

\section{From: Sean Cody}
A long time ago, in a galaxy... once upon a time... oh hell, congratulations on cracking this book. 
 If you are reading this book then in all probability you
are either interested in learning how to get better at using Unix tools or 
someone is forcing you to read this for credit.  In either case welcome.

This book was conceived under a particular frustration.  Throughout my
both academic and professional career I found myself working with very talented
people who had no idea how to use the tools in front of them.  This astonished
me because I can't conceive of basing a career on a black box.  I have to know
everything about everything from the bottom up to feel comfortable with my 
tools.  That being said, I'm not most people and the world is better for it.  
Instead while I was reading man pages and fighting compiler bugs other people 
where studying and doing well on their exams.  I am a terrible student but 
I love to tinker and break things.

In this vein the purpose of this book is to provide a shim between the hacker
mentality of making stuff go and the goal to `get things done.'

\section{From: Robert Guderian}

I, on the other hand, never really saw the value of digging into UNIX. I'm
a Computer Science student, and stayed on the coding side of things. 
I knew how to scratch by in UNIX to get the job done, but never saw
the benefit of knowing the platform I was using. And this worked, up to a point.
In retrospect, I wasn't using the tools I had at my disposal. I built a 
house with no foundation. Programming is 90\% thinking about the problem, and 10\%  actually
programming. Knowing what UNIX can do for you helps you think about your problem with a
proven toolkit in your back pocket.

This book was written assuming you've used a computer before... if not a UNIX terminal itself. 
I hope the pace is fast, but not overwhelming. My sole advice here is `shut up and try it'. 
It's really hard to learn this stuff without actually doing it.
